**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-03-08 Manuscripts/Manuscript_AM_v3.Rmd
Need to tweak the plot for the basis

```{r,basis-functions}
library(mgcv)
library(mvnfast)
  library(nlme)
  library(ggsci)
library(tidyverse)

@@

#length of dataframe to be created: number of knots by number of timepoints (minus 1 for the intercept that we won't plot)
ln<-length(basis1)*(length(coef(gm))-1)

basis_plot<-data.frame(Basis=integer(ln),
                       value=double(ln),
                       time=integer(ln),
)

basis_plot$time<-rep(time) #pasting timepoints
basis_plot$Basis<-rep(1:4,each=6) #pasting basis number values
basis_plot$value<-basis$value #pasting basis values

ggplot(basis_plot,aes(x=time,y=value))+geom_line()+facet_grid(~Basis) #plotting

#plot(dat$y~dat$time)

>>>>

```{r,basis-functions}
library(mgcv)
library(mvnfast)
  library(nlme)
library(patchwork)
  library(ggsci)
library(tidyverse)

@@

#length of dataframe to be created: number of knots by number of timepoints (minus 1 for the intercept that we won't plot)
ln<-6*(length(coef(gm))-1)

basis_plot<-data.frame(Basis=integer(ln),
                       value_orig=double(ln),
                       time=integer(ln),
                       cof=double(ln)
)

basis_plot$time<-rep(time) #pasting timepoints
basis_plot$Basis<-rep(1:4,each=6) #pasting basis number values
basis_plot$value_orig<-basis$value #pasting basis values
basis_plot$cof<-rep(coef(gm)[2:5],each=6) #pasting coefficients
basis_plot<-basis_plot%>%
  mutate(mod_val=value_orig*cof)

#calculating the final spline by aggregating the basis functions

spl<-basis_plot%>% group_by(time)%>%summarize(spl=sum(mod_val))

#original bases
p1<-ggplot(basis_plot,aes(x=time,y=value_orig,colour=factor(Basis)))+
  geom_line()+geom_point()+
  facet_grid(~Basis)+
  theme_classic()+
  scale_color_aaas()

#basis multiplied by the coefficient
p2<-ggplot(basis_plot,aes(x=time,y=mod_val,colour=factor(Basis)))+
  geom_line()+geom_point()+
  facet_grid(~Basis)+
  theme_classic()+
  scale_color_aaas()

#heatmap of the coefficient
p3<-ggplot(basis_plot,aes(x=Basis,y=Basis,fill=cof))+
  geom_tile(aes(color='black'),size=2)+
  geom_tile(size=2)+
  scale_fill_gradient(low = "white", high = "red")+ 
  geom_text(aes(label=round(cof,1)))+
  theme_classic()

p4<-ggplot(data=dat,aes(x=time,y=y))+
  geom_point()+
  geom_line(data=spl,aes(x=time,y=spl))+
  scale_color_aaas()+
  theme_classic()

p1+p2+p3+p4+plot_annotation(tag_levels='A')
#plotting
#plot(dat$y~dat$time)
